SunPy - Python for Solar Physics

### 2014-01-20 1-Introduction.tex
First draft for Dev and Future as well lc tweaks.
Changed to minted typesetting for code examples in lc section.

\section{Introduction}
SunPy is a project dedicated to providing the tools to process and analyse 
solar data in Python.
The Python programming language has gained much traction as a scientific 
programming language in the last decade.
Projects such as \texttt{NumPy}, \texttt{SciPy}, \texttt{matplotlib} provide 
the core tools needed for scientific analsysis and visualisation, while other 
packages such as pandas, Astropy or scikit-image provide more domain specific 
functionality. SunPy aims to provide such domain specific functionality to the 
solar physics community.

>>>>

\section{Introduction}
SunPy is a project dedicated to providing the tools to process and analyse 
solar data in Python.
The Python programming language has gained much traction as a scientific 
programming language in the last decade.
Projects such as \texttt{NumPy}, \texttt{SciPy}, \texttt{matplotlib} provide 
the core tools needed for scientific analysis and visualisation, while other 
packages such as pandas, Astropy or scikit-image provide more domain specific 
functionality. SunPy aims to provide such domain specific functionality to the 
solar physics community.
